---
title: "prague_colaborators"
author: "RRPS"
date: '2022-07-14'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
	fig.height = 5,
	fig.width = 8,
	dpi = 180,
	message = FALSE,
	warning = FALSE,
	cache = TRUE,
	echo = TRUE
)
```

```{r CLEAR EVERYTHING, eval=FALSE, include=FALSE}
# unload all non-base packages
lapply(names(sessionInfo()$otherPkgs), function(pkgs)
  detach(
    paste0('package:', pkgs),
    character.only = T,
    unload = T,
    force = T
))

rm(list=ls())
```

Need to start a new session to run this script due to gstat conflicts with other packages

```{r load libraries, message=FALSE, warning=FALSE, include=FALSE}
# load the packages
# main packs to start with
pcks <- c( "tidyverse", "janitor")
# require("tidyverse")

if(sum(as.numeric(!pcks %in% installed.packages())) != 0){
  installation <- pcks[!pcks %in% installed.packages()]
  for(i in 1:length(installation)) {
    install.packages(installation, dependencies = T)
    break()}
  suppressPackageStartupMessages(
  sapply(pcks,require,character.only = T)
) 
} else {
  suppressPackageStartupMessages(
  sapply(pcks,require,character.only = T)
) 
}

rm(pcks)
```

# setting working directories
```{r directories}
# get working directory and paste directory to save outputs
# in the Knit dropdown menu, select Knit directory, then Current Working Directory.
setwd('C:/Users/rrocha/Documents/R/microbiome_br/')
work_dir <- getwd()
folder_path <- paste0(work_dir, "/outputs")
data.dir <- paste0(work_dir, "/data/prague")
dir.create("data")
dir.create(data.dir)
setwd(data.dir)

# # set colors
# color_distance <- c("D0" = "deepskyblue2", 'D1' = 'brown1',  "D2" = "forestgreen", "D3" = "#440154FF", "D4" = "burlywood")
# # color_distance1 <- c('D1' = 'brown1',  "D2" = "forestgreen", "D3" = "#440154FF", "D4" = "burlywood")
# color_depth <- c('DP1'="darkorange",'DP2'="purple", "DP3" = "cyan4")
# color_sites <- c(lease_1 = "#56B4E9", lease_2 ="#E69F00"  , Control =  "#009E73", other_leases = "#D1BCA8")

# check the working directory
paste("Working in directory:", getwd())
```

# data

if the status in "Complete Genome" < 8: get the biggest Status. if > 8: make 3 column with Q1, median, and Q3 and count the genomes.
If there isn´t Complete Genome > Scaffold > Contig > Chromosome 

```{r get the data}
# eukaryotic table
euk <- read_delim('eukaryotes.txt')
euk.clean <- euk %>% 
  mutate(`#Organism/Name` = str_replace_all(`#Organism/Name`, "\\[|\\]","")) %>% 
  mutate(Organism = `#Organism/Name`, .after = `#Organism/Name`) %>%
  janitor::clean_names(.)

# take a look in the data
euk.clean %>% filter(if_any(everything(), ~str_detect(., "Candida albicans"))) %>% pull(status, organism)

# prokaryotic table
prok <- read_delim('prokaryotes.txt')
prok.clean <- prok %>% 
  mutate(`#Organism/Name` = str_replace_all(`#Organism/Name`, "\\[|\\]","")) %>% 
  mutate(Organism = `#Organism/Name`, .after = `#Organism/Name`) %>%
  janitor::clean_names(.)

#prok %>% slice(102225)

# lets take a look in the databases
prok.clean %>% filter(if_any(everything(), ~str_detect(., "Koribacter versatilis Ellin345"))) %>% 
  filter(if_any(status, ~str_detect(., "Complete")))

prok %>% filter(if_any(everything(), ~str_detect(., "Candidatus")))

# table final
final.table <- read_delim('MG_FEDERICA_TABLE_FINAL.tab')

# it removes any instance of '[' or ']'
table.clean <- final.table %>% 
  mutate(BEST_TAX = str_replace_all(BEST_TAX, "\\[|\\]","")) %>% 
  rename('number_organism_name' = 'BEST_TAX') %>%
  mutate(organism = number_organism_name, .after = number_organism_name) %>%
  clean_names()

table.clean %>% select(number_organism_name) %>% filter(if_any(everything(), ~str_detect(., "Candidatus")))

# get the taxonomies
taxonomies <- table.clean %>% filter(number_organism_name != "-") %>% pull(number_organism_name) %>% as.factor() %>% levels()

rm(euk,prok)

```

Extract the information based on the texonomies
For prokaryotes 
```{r}
# filter prok table
prok.info <- prok.clean %>% 
              select(number_organism_name, organism, size_mb, gc_percent, status) %>% 
              mutate(gc_percent = as.numeric(gc_percent))
best_tax_prok <- taxonomies %>% map_df(., ~prok.info  %>% 
                                               filter(str_detect(organism, .x)) %>% 
                                               mutate(taxonomy = .x)
                                       )
# Store hits found

write.table(x = best_tax_prok, file = "federica_found_taxonomy_prok.txt", quote = F, sep = "\t", row.names = F)

## read hits found. Avoid running all steps again.
# best_tax_prok <- read_delim(file = "federica_found_taxonomy_prok.txt")

# Checking for differences between organism name and Taxonomy from FEDERICA's table
options(pillar.print_max = 10, pillar.print_min = 10, pillar.width = 35)

which(best_tax_prok$number_organism_name != best_tax_prok$taxonomy)
best_tax_prok[which(best_tax_prok$number_organism_name != best_tax_prok$taxonomy), c(1,6)]

```


For eukaryotes
```{r}
# filter euk table
euk.info <- euk.clean %>% 
              select(number_organism_name, organism, size_mb, gc_percent, status) %>% 
              mutate(gc_percent = as.numeric(gc_percent))
# Indentify taxa without GC content info (353 found)
euk.info[which(is.na(euk.info$gc_percent)),]

best_tax_euk <- taxonomies %>% map_df(., ~euk.info  %>% 
                                              filter(str_detect(organism, .x)) %>% 
                                              mutate(taxonomy = .x)
                                      )
# Store euk hits found
write.table(x = best_tax_euk, file = "federica_found_taxonomy_euk.txt", quote = F, sep = "\t", row.names = F)

## Read hits found. Avoid running all steps again.
best_tax_euk <- read_delim(file = "federica_found_taxonomy_euk.txt")

# all.info <- euk.info %>% bind_rows(prok.info)
```

Split the datasets based on status
For prokayotes

```{r}
table_summ_prok <- best_tax_prok %>% 
 select(taxonomy, status, size_mb, gc_percent) %>%
  group_by(taxonomy, status) %>% 
  skimr::skim(size_mb, gc_percent) %>%
  left_join(best_tax_prok %>% 
              group_by(taxonomy, status) %>% 
              summarise(n_size_mb = n_distinct(size_mb),
                        n_gc_percent = n_distinct(gc_percent))
            )

table_summ_prok %>% distinct(skim_variable)
```

```{r}
# status
best_tax_prok %>% distinct(status)
# best_tax_prok_complete_genome <- best_tax_prok %>% filter(status == 'Complete Genome')
# best_tax_prok_scaffold <- best_tax_prok %>% filter(status == 'Scaffold')
# best_tax_prok_contig <- best_tax_prok %>% filter(status == 'Contig')
# best_tax_prok_chromosome <- best_tax_prok %>% filter(status == 'Chromosome')

# best_tax_prok %>% summarise(mean_size_mb = mean(size_mb),
                    #           max_size_mb = max(size_mb),
                    #           min_size_mb = min(size_mb),
                    #           n_size_mb = n_distinct(size_mb)
                    #           ) %>%
  # filter(n_size_mb >= 3)
```

```{r}
# Create function to gather statistics about the genomic information, using the highest level of assembly and the longer assembly

number_of_entries <- best_tax_prok %>% count(taxonomy)

# See the taxa with the most entries

number_of_entries[order(number_of_entries$n,decreasing = T),]

## Tests
# taxa = "Xanthomonas campestris pv. campestris" # 80
# taxa = "Cronobacter turicensis" # 16
# taxa = "Acetobacter pasteurianus IFO 3283-32" # 1
# taxa = "Acetobacter pasteurianus IFO 3283-01" # 2
# 
# match("Acetobacter pasteurianus IFO 3283-32", number_of_entries$taxonomy)
# number_of_entries[match(taxa, number_of_entries$taxonomy), "n"]
# test_entries <- number_of_entries[match(taxa, number_of_entries$taxonomy), "n"]

## The function
genomic_traits <- function(taxa){
  
  Assembly_level <- c("Complete Genome","Chromosome","Scaffold","Contig")
  
  number_of_entries_in_genomic_db <- number_of_entries[match(taxa, number_of_entries$taxonomy),"n"]
   
  size_gc_status <-
    best_tax_prok[which(!is.na(match(best_tax_prok$taxonomy,taxa))),c("size_mb","gc_percent","status")] %>%
    mutate(number_of_entries_in_NCBI = as.numeric(number_of_entries_in_genomic_db))
  
  Higher_status <- Assembly_level[min(match(size_gc_status$status,Assembly_level))]
  
  used_genomes <- size_gc_status %>% 
    filter(status == Higher_status)
  
  number_of_genomes_after_filter <- nrow(used_genomes)
    
  summ_entries <- do.call(cbind, lapply(used_genomes[,1:2], summary))
      
    
  df_summ_entries <- data.frame(size_mb_min = summ_entries[1,1],
                                  size_mb_1st_qtl = summ_entries[2,1],
                                  size_mb_median = summ_entries[3,1],
                                  size_mb_3rd_qtl = summ_entries[4,1],
                                  size_mb_max = summ_entries[5,1],
                                  gc_content_min = summ_entries[1,2],
                                  gc_content_1st_qtl = summ_entries[2,2],
                                  gc_content_median = summ_entries[3,2],
                                  gc_content_3rd_qtl = summ_entries[4,2],
                                  gc_content_max = summ_entries[5,2]
                                  )
    
  genome_stats_table <- used_genomes %>% 
    select(-status) %>%
    mutate(df_summ_entries) %>%
    mutate(highest_assembly_level = Higher_status, .after = gc_percent ) %>%
    mutate(Taxonomy = taxa, .before = size_mb) %>%
    mutate(number_of_genomes_with_highest_assembly_level = number_of_genomes_after_filter, .before = size_mb_min)
    
  genome_stats_table %>% 
      slice(which.max(size_mb))
  }

# Testing function
taxa = "Cronobacter turicensis" # 16

c(genomic_traits(taxa)) %>%
  as.data.frame()

# check on the larger ones from the table
taxonomy_search_using_apply <- lapply(X = number_of_entries$taxonomy[order(number_of_entries$n, decreasing = F)][1100:1163], FUN = genomic_traits)
removed_list <- as_tibble(do.call(rbind,taxonomy_search_using_apply))

```

For eukayotes
```{r}
# status
best_tax_euk %>% distinct(status)
table_summ_euk <- best_tax_euk %>% 
 select(taxonomy, status, size_mb, gc_percent) %>%
  group_by(taxonomy, status) %>% 
  skimr::skim(size_mb, gc_percent) %>%
  left_join(best_tax_euk %>% 
              group_by(taxonomy, status) %>% 
              summarise(n_size_mb = n_distinct(size_mb),
                        n_gc_percent = n_distinct(gc_percent))
            )

# table_summ_euk %>% distinct(skim_variable)
# 
# best_tax_euk %>% filter(taxonomy == "Alternaria alternata" & status == "Contig") %>%
#   group_by(taxonomy, status) %>%
#    summarise(n_size_mb = n_distinct(size_mb),
#                         n_gc_percent = n_distinct(gc_percent)) 

best_tax_euk %>% 
              group_by(taxonomy, status) %>% 
              summarise(n_size_mb = n_distinct(size_mb),
                        n_gc_percent = n_distinct(gc_percent)) %>%
              filter(n_size_mb >= 3) 

```
Add tax genome size and GC content to table Federica

```{r}

```
